### 2025-02-24 paper/performance.tex
Another performance remark.

>>>>

Closing this performance gap could be done by improving the Futhark
compiler to match cuDNN's performance, although this is perhaps not
realistic. Another approach could be to extract TensorFlow instead of
Futhark from our DSL, although this will also require us to add new
builtin primitives to perform e.g. convolutions, as our index-oriented
array operations are not a good fit for TensorFlow's programming
model. Although not difficult to do, and it would result in better
performance for the specific case of CNNs, it would result in a more
restricted language, which is less interesting from a research
perspective.
